%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}    
%---------------------------------------------------------
  \cventry
    {University of Pretoria} % Organisation
    {Honours Research Project (mark: 94/100)} % Project
    {Pretoria, South Africa} % Location
    {Feb 2025 - November 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Research report titled: A Python Library for Explainable Problem Landscape Analysis.}
        \item {Developed a Python library for Explainable Landscape Analysis (xLA) comprising 17 xLA features.}
        \item {Showed that the developed library is effective for xLA.}
        \item {\textbf{Technical Skills:} PyTorch, Google Colab, Python}
      \end{cvitems}
    }

  \cventry
    {University of Pretoria} % Organisation
    {Natural Language Processing module} % Project
    {Pretoria, South Africa} % Location
    {Feb 2025 - June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Semester research report titled: Meta-learning for Semantic Relatedness: A Comparative Study of Meta-Learning and Transfer Learning for Semantic Relatedness Tasks in African Languages using the SemRel2024 Dataset.}
        \item{Aim: determine whether meta-learning (model-agnostic meta-learning) could outperform transfer learning in low-resourced African languages STR tasks.}
        \item {Showed that transfer learning outperformed the meta-learning approach.}
        \item {\textbf{Technical Skills:} PyTorch, Google Colab, Python}
      \end{cvitems}
    }

    \cventry
        {Strathmore University} % Organisation
        {Undergraduate Final Research Project (mark: 81.94)} % Project
        {Nairobi, Kenya} % Location
        {Apr 2022 - Dec 2022} % Date(s)
        {
          \begin{cvitems} % Description(s) of project
            \item {Developed a deep learning model for segmentation and classification of melanoma skin cancer lesions.}
            \item {Carried out a comparative study of fine-tuning 6 neural network architectures: ResNet34, ResNet50, ResNet152, InceptionV3, VisionTransformer, and EfficientNet-B7.}
            \item {Trained on an ensemble dataset of 5 different medical image datasets: MED-NODE, PAD-UFES-20, 7-point, DermIS, and DermQuest.}
            \item {Developed mobile app for taking and uploading photos of skin lesions to a RESTful API for inference.}
            \item Sep 2024: Recognised as a 2024 Highly Commended Entrant and subsequently as the 2024 Africa and the Middle East Regional Winner by the Global Undergraduate Awards.
            \item Published on The Global Undergraduate Award Library (\href{https://gua.soutron.net/Portal/Default/en-GB/RecordView/Index/3205}{HERE})
            \item {\textbf{Technical Skills:} PyTorch, Flask, SQLite, React Native, Google Colab, Python, Talend}
          \end{cvitems}
        }
%---------------------------------------------------------
\end{cventries}
