%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteering}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mentor} % Job title
    {Strathmore University} % Organisation
    {Nairobi, Kenya} % Location
    {Sep 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentoring 5 undergraduate students pursuing undergraduate degrees in Computer Science.}
        \item {Mentoring involves informal meetings with each mentee one-on-one to accompany them with decisions in their life.}
        \item {\textbf{Skills:} Mentoring, Coaching}
      \end{cvitems}
    }
    
  \cventry
    {Member} % Job title
    {Mbagathi Study Center} % Organisation
    {Nairobi, Kenya} % Location
    {Jan 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organised 5 charity visits to 6 charity organisations attending to vulnerable groups such as orphans and the elderly to donate food, and clothing and undertake voluntary work}
        \item {Mentored 4 students of Lenana High School.}
        \item {\textbf{Skills:} Leadership, Mentoring}
      \end{cvitems}
    }
    
  \cventry
    {Secretary} % Job title
    {Mbagathi Study Center} % Organisation
    {Nairobi, Kenya} % Location
    {Jan 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinating the mentorship activities for university students:}
        \item Organised 3 weekend-long character seminars
        \item Organised 9 charity visits to charitable organisations attending to vulnerable groups
        \item Organised 1 conference for university students on the impact of AI on our humanity.
        \item {Mentoring 4 students of Lenana High School.}
        \item {Giving class on virtuous leadership}
        \item {\textbf{Skills:} Leadership, Mentoring, Coaching}
      \end{cvitems}
    }
    
  \cventry
    {Assistant Teacher} % Job title
    {Langata Road Primary School} % Organisation
    {Nairobi, Kenya} % Location
    {Feb 2022 - Mar 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught primary-level Mathematics, English, Writing, Social Studies and Computing Devices.}
        \item {Mentored 4 boys in the school on a one-on-one basis.}
        \item {Marked pupils' scripts and compiled marksheets.}
        \item {Served as a teacher on duty for a week.}
        \item {\textbf{Skills:} Leadership, Mentoring, Teaching, Public Speaking}
      \end{cvitems}
    }
\end{cventries}
